### 2025-07-13 conteudo/apendices/students-artifacts.tex
some work from 04-06
update students apendix

@@

@@

@@

@@

@@

@@

\textbf{Blog 1:} \url{https://o-carneiro.github.io/}

\textbf{Blog 2:} \url{https://fernandoglima.github.io/}

\textbf{Blog 3:} \url{https://eijiuchiyama.github.io/softwarelivre/}

\paragraph{Group 12}

@@

>>>>

\textbf{Accepted PATCH (v1):} \url{https://lore.kernel.org/linux-iio/20250424002144.23260-1-beatrizvianacosta16@gmail.com/}

@@

\textbf{Accepted PATCH (v3):} \url{https://lore.kernel.org/linux-iio/20250426163311.546500bc@jic23-huawei/}

@@

\textbf{Accepted PATCH (v1):} \url{https://lore.kernel.org/linux-iio/20250426153307.59689da0@jic23-huawei/T/#t}

@@

\textbf{Accepted PATCH (v3):} \url{https://lore.kernel.org/linux-iio/20250531160807.39e54096@jic23-huawei/}

@@

\textbf{PATCH in Linux lore:} \url{https://lore.kernel.org/all/20250422191114.32832-1-nattanferreira58@gmail.com/#t}

\textbf{Accepted PATCH (v4):} \url{https://lore.kernel.org/all/20250614124401.32b17eda@jic23-huawei/}

@@

\textbf{Accepted PATCH (partially accepted on v6):} \url{https://lore.kernel.org/linux-iio/20250621183843.2f8bcb48@jic23-huawei/}

@@

@@

\textbf{Accepted PATCH (v2):} \url{https://lore.kernel.org/amd-gfx/CADAW+GDN-4Lwd87h793csWF6r5cgqpgrpEPzRyDV9+rfkNPmTA@mail.gmail.com/}
